Pen-pneumo

### 2017-02-03 states/resistance/penicillin-pneumococcus/penicillin-pneumo-report.Rmd
kable

```{r echo=FALSE}

library(broom)

@@

```{r echo=FALSE}
bug_drug
```

```{r echo=FALSE, message=FALSE}
abg = read_tsv('../../../../../antibiogram/data/abg.tsv') %>%
  mutate(drug=tolower(drug)) %>%
  rename(resistance_drug=drug)

>>>>

```{r echo=FALSE}
library(knitr)
library(broom)

@@

```{r echo=FALSE, result='asis'}
bug_drug %>% kable
```

```{r echo=FALSE, message=FALSE, cache=TRUE}
abg = read_tsv('../../../../../antibiogram/data/abg.tsv') %>%
  mutate(drug=tolower(drug)) %>%
  rename(resistance_drug=drug)
